### 2022-12-28 paper.tex
REFACTOR: Adjust semester, author and title
REFACTOR: Adjust introduction and references

% ---------------------------------------------------------------------
\captionsetup{labelfont=bf,textfont=it}
\title[Fancy 3D Animation Demo]%
      {Fancy Paper in the Field of Visual Computing}

\author[U. Schwanecke]
    {\parbox{\textwidth}
        {\centering 
			U. Schwanecke
        }
        \\
    {\parbox{\textwidth}
        {\centering RheinMain University of Applied Sciences, Wiesbaden, Germany\\
       }
    }
}
% ------------------------------------------------------------------------

@@

%-------------------------------------------------------------------------
\section{Introduction}
\label{sec:introduction}
Some nice introduction, e.g. citing some literature such as \cite{Tjaden2017, Achenbach2018, Sommer2020} \ldots

$$
\sum_{i=1}^n i = \frac{n(n+1)}{2}
$$
\blindtext

>>>>

% ---------------------------------------------------------------------
\captionsetup{labelfont=bf,textfont=it}
\title[Burst Images]%
      {Burst Images}

\author[Sascha Scheid]
    {\parbox{\textwidth}
        {\centering 
			Sascha Scheid
        }
        \\
    {\parbox{\textwidth}
        {\centering RheinMain University of Applied Sciences, Wiesbaden, Germany\\
       }
    }
}
% ------------------------------------------------------------------------

@@

%-------------------------------------------------------------------------
\section{Introduction}
\label{sec:introduction}

Burst photography is a technique in which a series of photographs is taken quickly in succession.
This can be useful in a variety of situations, such as capturing action or movement, 
or to create a sense of motion. In digital photography, burst images are stored as a 
sequence of image files, typically in a format such as JPEG or RAW.

High Dynamic Range (HDR) is a technique used to improve the dynamic range of an image, 
which is the range of luminance or brightness levels that can be captured in a photograph. 
The dynamic range of a scene can often be greater than what a camera is able to capture 
in a single image, resulting in lost detail in the highlights or shadows. 
HDR techniques can be used to extend the range of luminance in an image, 
resulting in more detail and a more realistic representation of the scene.

One way that burst photography and HDR techniques can be used together in mobile cameras 
is to capture a series of photographs with different exposures in a burst, and then combine 
the exposures into a single HDR image using software. This can be particularly useful in 
low-light situations, where the camera may struggle to capture a wide range of luminance 
levels in a single exposure. By capturing multiple exposures and combining them into an 
HDR image, it is possible to extend the dynamic range and capture more detail in both the 
highlights and shadows.

\cite{Hasinoff2016Burst}
